Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-10-29 documentation/paper.tex
Included exact dates and times for example data
Included CAD of the PICO-60 detector
Removed line numbers
Added description of detector

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{caption}
\usepackage{lineno}
\linenumbers

@@

@@

@@

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{audio}
    \caption{\label{} An example of the audio waveform $\omega$ with initial background and hydraulic noise cropped (left) and the resulting full resolution Fourier transform $\beta_{50,001}$ (right) for both audio channels. Recorded on 2016-12-02, run 1, event 21.}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{image_grid}
    \caption{\label{} An example of the image sequence $\iota$. Recorded on 2016-09-23, run 4, event 33.}
\end{figure}

>>>>

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{caption}

@@

\subsubsection{Introduction}

@@

\subsubsection{About the Detector}

The detector was filled with 52 kg of liquid C$_3$F$_8$, which was held at a constant temperature by a large chilled water bath. The pressure of the target liquid, held inside a synthetic quartz inner vessel, was very accurately controlled with propylene glycol as hydraulic fluid inside a stainless steel pressure vessel (Figure \ref{pico_cad}).

The target was superheated by reducing its pressure until it entered a metastable state in which the vapor phase became energetically accessible. In the presence of a sufficiently dense energy deposition, a bubble would be nucleated and would grow to visible size. Four cameras stereoscopically monitored the chamber for these bubbles, issuing a recompression trigger upon their appearance. At this time, acoustic traces are recorded that capture the sound of bubble formation. The rising pressure caused the vapor bubble to condense as the fluid reverted to a non-superheated state. Following this, the hydraulic system prepared to return the detector to the sensitive superheated state by once again expanding to a lower pressure.

Alpha decays along the U/Th chains present the dominant remaining background which must be distinguished from nuclear recoils acoustically.

\subsubsection{Properties of Events}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{pico_cad}
    \caption{\label{pico_cad} CAD rendering of the PICO-60 detector as configured for its operation with C$_3$F$_8$.}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{audio}
    \caption{\label{} An example of the audio waveform $\omega$ with initial background and hydraulic noise cropped (left) and the resulting full resolution Fourier transform $\beta_{50,001}$ (right) for both audio channels. Recorded on 2016-12-03 at 04:22:45 UTC.}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{image_grid}
    \caption{\label{} An example of the image sequence $\iota$. Recorded on 2016-09-23 at 22:15:44 UTC.}
\end{figure}
